Project Report\\\textsc{DEVS Ex Machina}

### 2015-05-23 manual/tex/models.tex
* added a tiny bit about the cell atomic model to the manual
Signed-off-by: Lttlemoi <lttlemoi+git@gmail.com>

>>>>

\subsection{Cell Atomic Model}
The \texttt{CellAtomicModel} is a specialized atomic model that provides functionality for the cell tracer. It is useful when models are laid out in a grid. This class extends the interface of the atomic model with methods for getting or setting the position of this model in the grid.
